### 2019-09-23 MTech/CS553/HW3/HW3_11910230.tex
HW3: Made corrections in Q2

\subsection{Inverse Key}
$|K|$ = $11\times7-3\times8$ mod 26 = 53 mod 26 = 1.\\
Adjoint of K
= $\begin{pmatrix}
7&-8\\-3&11
\end{pmatrix}$.
$\therefore K^{-1}$
= $\dfrac{1}{|K|}\times$ Adjoint of K 
=$\begin{pmatrix}
7&-8\\-3&11
\end{pmatrix}$

\subsection{Invertible?}
K can be said to be invertible only if $|K| \ne$ 0. Since $|K|$ = 53 $\ne$ 0, K is invertible.

\subsection{Decryption}
We calculated y
= $\begin{pmatrix}
21&0\\23&8
\end{pmatrix}$. Now, $x$ = $d_K(y)$ = $yK^{-1}$.\\
$\therefore y$
=$\begin{pmatrix}
21&0\\23&8
\end{pmatrix}
\begin{pmatrix}
7&-8\\-3&11
\end{pmatrix}$
=$\begin{pmatrix}
21\times7+0\times(-3) & 21\times(-8)+0\times11\\
23\times7+8\times(-3) & 23\times(-8)+8\times11
\end{pmatrix}$mod 26\\
= $\begin{pmatrix}
147&-168\\137&-96
\end{pmatrix}$ mod 26
= $\begin{pmatrix}
17&14\\7&8
\end{pmatrix}$ = \{R,O,H,I\}.\\
$\therefore x$ = $d_K(y)$ = ROHI.

>>>>

\subsection{Inverse Key}
$|K|$ = $(11\times7-3\times8)$ mod 26 = 53 mod 26 = 1.\\
Adjoint of K
= $\begin{pmatrix}
7&-8\\-3&11
\end{pmatrix}$.
$\therefore K^{-1}$
= $\left( \dfrac{1}{|K|}\times \text{Adjoint of K} \right)$ mod 26

=$\begin{pmatrix}
7&-8\\-3&11
\end{pmatrix}$ mod 26
=$\begin{pmatrix}
7&18\\23&11
\end{pmatrix}$

\subsection{Invertible?}
K can be said to be invertible only if $|K| \ne$ 0 and $gcd(|K|,26) = 1$. Since $|K|$ = 53 $\ne$ 0 and $gcd(53,26) = 1$, K is invertible.

\subsection{Decryption}
We calculated y
= $\begin{pmatrix}
21&0\\23&8
\end{pmatrix}$. Now, $x$ = $d_K(y)$ = $yK^{-1}$.\\
$\therefore y$
=$\begin{pmatrix}
21&0\\23&8
\end{pmatrix}
\begin{pmatrix}
7&18\\23&11
\end{pmatrix}$
=$\begin{pmatrix}
21\times7+0\times23 & 21\times18+0\times11\\
23\times7+8\times23 & 23\times18+8\times11
\end{pmatrix}$mod 26\\
= $\begin{pmatrix}
147&378\\137&502
\end{pmatrix}$ mod 26
= $\begin{pmatrix}
17&14\\7&8
\end{pmatrix}$ = \{R,O,H,I\}.\\
$\therefore x$ = $d_K(y)$ = ROHI.
